%%%%%%%%%%%%%%%%%%%%%%%% referenc.tex %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% sample references
% "computer science"
%
% Use this file as a template for your own input.
%
%%%%%%%%%%%%%%%%%%%%%%%% Springer-Verlag %%%%%%%%%%%%%%%%%%%%%%%%%%
%
% BibTeX users please use
% \bibliographystyle{}
% \bibliography{}
%
% Non-BibTeX users please use
\begin{thebibliography}{99.}
%
% and use \bibitem to create references.
%
% Use the following syntax and markup for your references
%
%% Monographs
%\bibitem{monograph} Kajan E (2002)
%Information technology encyclopedia and acronyms. Springer, Berlin
%Heidelberg New York
%
%% Contributed Works
%\bibitem{contribution} Broy M (2002) Software engineering -- From
%auxiliary to key technologies. In: Broy M, Denert E (eds)
%Software Pioneers. Springer, Berlin Heidelberg New York
%
%% Journal
%\bibitem{journal} Che M, Grellmann W, Seidler S (1997)
%Appl Polym Sci 64:1079--1090
%
%\bibitem{journal} Chde M, Grellmann W, Seidler S (1997)
%Appl Polym Sci 64:1079--1090
%
%%% Theses
%%\bibitem{thesis} Ross DW (1977) Lysosomes and storage diseases. MA
%%Thesis, Columbia University, New York
%
\bibitem{Asur} Asur, S., S. Parthasarathy, and D. Ucar, (2009), ``\textit{An event-based framework for characterizing the evolutionary behavior of interaction graphs,}'' ACM Trans.  Knowledge Discovery Data. 3, 4, Article 16, (November 2009), 36 pages. 2009.

\bibitem{AzarbakhtOSS2014} Azarbakht, A. and C. Jensen, ``\textit{Drawing the Big Picture: Temporal Visualization of Dynamic Collaboration Graphs of OSS Software Forks,}'' Proc. 10th Int'l. Conf. Open Source Systems, 2014.

\bibitem{AzarbakhtINSNA2014} Azarbakht, A. and C. Jensen, ``\textit{Temporal Visualization of Dynamic Collaboration Graphs of OSS Software Forks,}'' Proc. Int'l. Network for Social Network Analysis (INSNA) Sunbelt XXXIV Conf., 2014.

\bibitem{AzarbakhtOpenSym2013} Azarbakht, A., ``\textit{Drawing the Big Picture: Analyzing FLOSS Collaboration with Temporal Social Network Analysis,}'' Proc. 9th Int'l. Symp. Open Collaboration, ACM, 2013.

\bibitem{AzarbakhtOSS2013} Azarbakht, A. and C. Jensen, ``\textit{Analyzing FOSS Collaboration \& Social Dynamics with Temporal Social Networks,}'' Proc. 9th Int'l. Conf. Open Source Systems Doct. Cons., 2013.

\bibitem{AzarbakhtVLHCC2014} Azarbakht, A., ``\textit{Temporal Visualization of Collaborative Software Development in FOSS Forks,}'' Proc. IEEE Symp. Visual Languages and Human-Centric Computing, 2014.

\bibitem{Baishakhi} Baishakhi R., C. Wiley, and M. Kim, ``\textit{REPERTOIRE: a cross-system porting analysis tool for forked software projects,}'' Proc. ACM SIGSOFT 20th Int'l. Symp. Foundations of Software Engineering, ACM, 2012.

\bibitem{Bastian} Bastian, M., S. Heymann, and M. Jacomy, ``\textit{Gephi: an open source software for exploring and manipulating networks,}'' Int'l AAAI Conf. on Weblogs and Social Media, 2009.

\bibitem{Bezrukova} Bezrukova, K,, C. S. Spell, J. L. Perry, ``\textit{Violent Splits Or Healthy Divides? Coping With Injustice Through Faultlines,}'' Personnel Psychology, Vol 63, Issue 3. 2010. 

\bibitem{Bird} Bird, C., D. Pattison, R. D'Souza, V. Filkov, and P. Devanbu, ``\textit{Latent social structure in open source projects,}'' Proc. 16th ACM SIGSOFT Int'l. Symposium on Foundations of software engineering, ACM, 2008.  

\bibitem{Brandes} Brandes, U. ``\textit{A Faster Algorithm for Betweenness Centrality}'', Journal of Mathematical Sociology 25(2):163-177, 2001.

\bibitem{Chakrabarti} Chakrabarti,  D., and C. Faloutsos. ``\textit{Graph mining: Laws, generators, and algorithms,}'' ACM Computing Surveys, 38, 1, Article 2, 2006.

\bibitem{Coleman1964} Coleman, J.S. ``\textit{Introduction to Mathematical Sociology,}'' New York etc.: The Free Press of Glencoe. 1964.

\bibitem{CrowstonFLOSSWhatWeKnow} 
Crowston, K., K. Wei, J. Howison, and A. Wiggins. ``\textit{Free/Libre open-source software development: What we know and what we do not know,}'' ACM Computing Surveys, 44, 2, Article 7, 2012.

\bibitem{DavidsonVLHCC2014} Davidson, J, R. Naik, A. Mannan, A. Azarbakht, C. Jensen, ``\textit{On older adults in free/open source software: reflections of contributors and community leaders,}'' Proc. IEEE Symp. Visual Languages and Human-Centric Computing, 2014.

\bibitem{Ernst} Ernst, N., S. Easterbrook, and J. Mylopoulos, ``\textit{Code forking in open-source software: a requirements perspective,}'' arXiv preprint arXiv:1004.2889, 2010.

\bibitem{Ford} Ford, L. R. and D. R. Folkerson, ``\textit{A simple algorithm for finding maximal network flows and an application to the Hitchcock problem,}'' Canadian Journal of Mathematics, vol. 9, pp. 210-218, 1957. 

\bibitem{Forrest} Forrest, D., C. Jensen, N. Mohan, and J. Davidson, ``\textit{Exploring the Role of Outside Organizations in Free/ Open Source Software Projects,}'' Proc. 8th Int'l. Conf. Open Source Systems, 2012.

\bibitem{Fruchterman} Fruchterman, T. M. J. and E. M. Reingold, ``\textit{Graph drawing by force-directed placement,}'' Softw: Pract. Exper., vol. 21, no. 11, pp. 1129-1164, 1991.

\bibitem{Guzzi} Guzzi, A., A. Bacchelli, M. Lanza, M. Pinzger, and A. van Deursen. ``\textit{Communication in open source software development mailing lists,}'' Proc. 10th Conf. on Mining Software Repositories, IEEE Press, 2013.

\bibitem{Hannemann} Hannemann, A and , R. Klamma ``\textit{Community Dynamics in Open Source Software Projects: Aging and Social Reshaping,}'' Proc. Int. Conf. on Open Source Systems, 2013. 

\bibitem{Heider} Heider, F. The Psychology of Interpersonal Relations. John Wiley \& Sons. 1958.

\bibitem{HowisonPerilsSourceForge} Howison, J. and K. Crowston. ``\textit{The perils and pitfalls of mining SourceForge,}'' Proc. Int'l. Workshop on Mining Software Repositories, 2004.  

\bibitem{HowisonSocialDynamics} Howison, J., K. Inoue, and K. Crowston, ``\textit{Social dynamics of free and open source team communications,}'' Proc. Int'l. Conf. Open Source Systems, 2006.  

\bibitem{HowisonFlossMole} Howison, J., M. Conklin, and K. Crowston, ``\textit{FLOSSmole: A collaborative repository for FLOSS research data and analyses,}'' Int'l. Journal of Information Technology and Web Engineering, 1(3), 17-26. 2006.

\bibitem{Krivitsky} Krivitsky, P. N., and M. S. Handcock. ``\textit{A separable model for dynamic networks,}'' Journal of the Royal Statistical Society: Series B (Statistical Methodology) 76, no. 1: 29-46. 2014.

\bibitem{Kuechler} Kuechler, V., C. Gilbertson, and C. Jensen, ``\textit{Gender Differences in Early Free and Open Source Software Joining Process,}'' Open Source Systems: Long-Term Sustainability, 2012. 

\bibitem{Kunegis} Kunegis, J., S. Sizov, F. Schwagereit, and D. Fay, ``\textit{Diversity dynamics in online networks,}'' Proc. 23rd ACM Conf. on Hypertext and Social Media, 2012. 

\bibitem{LeskovecGraphsOverTime} Leskovec, J., Kleinberg, J., and Faloutsos, C.: ``\textit{Graphs over time: densification laws, shrinking diameters and possible explanations,}'' Proc. SIGKDD Int'l. Conf. Knowledge Discovery and data Mining, 2005. 

\bibitem{LeskovecStatisticalPropertiesOfCommunityStructure} Leskovec, J., K. J. Lang, A. Dasgupta, and M. W. Mahoney, ``\textit{Statistical properties of community structure in large social and information networks,}'' Proc. 17th Int'l. Conf. World Wide Web, ACM, 2008.  

\bibitem{Nakakoji} Nakakoji, K., Y. Yamamoto, Y. Nishinaka, K. Kishida, and Y. Ye. ``\textit{Evolution patterns of open-source software systems and communities,}'' Proc. Int'l. Workshop Principles of Software Evolution, ACM, 2002.

\bibitem{NymanToForkOrNotToFork} Mikkonen, T., L. Nyman, ``\textit{To Fork or Not to Fork: Fork Motivations in SourceForge Projects,}'' Int'l. J. Open Source Softw. Process. 3, 3. July, 2011.

\bibitem{Noack} Noack, A., ``\textit{Energy models for graph clustering,}'' J. Graph Algorithms Appl., vol. 11, no. 2, pp. 453-480, 2007.

\bibitem{Nowak} Nowak, M. A. ``\textit{Five rules for the evolution of cooperation,}'' Science 314, No. 5805: 1560-1563. 2006.

\bibitem{NymanCodeForking} Nyman, L. , ``\textit{Understanding code forking in open source software,}'' Proc. 7th Int'l. Conf. Open Source Systems Doct. Cons., 2011. 

\bibitem{NymanForkingSustainability} Nyman, L., T. Mikkonen, J. Lindman, and M. Foug\`{e}re, ``\textit{Forking: the invisible hand of sustainability in open source software,}'' Proc. SOS 2011: Towards Sustainable Open Source, 2011. 

\bibitem{NymanHackersForking} Nyman, L., ``\textit{Hackers on Forking,}'' Proc. Int'l. Symp. on Open Collaboration, 2014. 

\bibitem{Oh} Oh, W., Jeon, S., ``\textit{Membership Dynamics and Network Stability in the Open-Source Community: The Ising Perspective}'' Proc. 25th Int'l. Conf. Information Systems. 2004.

\bibitem{Page} Page, B, B. Sergey, R. Motwani and T. Winograd, ``\textit{The PageRank Citation Ranking: Bringing Order to the Web,}'' Technical Report, Stanford InfoLab, 1999.

\bibitem{Robins} Robins, G., P. Pattison, Y. Kalish, and D. Lusher. ``\textit{An introduction to exponential random graph (p*) models for social networks,}'' Social networks 29, no. 2: 173-191. 2007.

\bibitem{Robles} Robles, G. and J. M. Gonzalez-Barahona, ``\textit{A comprehensive study of software forks: Dates, reasons and outcomes,}'' Proc. 8th Int'l. Conf. Open Source Systems, 2012. 

\bibitem{Rocchini} Rocchini, C. (Nov. 27 2012), Wikimedia Commons, Available:\\ http://en.wikipedia.org/wiki/File:Centrality.svg, 2012.  

\bibitem{Singer} Singer, L., F. Figueira Filho, B. Cleary, C. Treude, M. Storey, and K. Schneider. ``\textit{Mutual assessment in the social programmer ecosystem: an empirical investigation of developer profile aggregators,}'' Proc. Conf. Computer supported cooperative work, ACM, 2013.

\bibitem{SnijdersMCMCMLE} Snijders, T. AB. ``\textit{Markov chain Monte Carlo estimation of exponential random graph models,}'' Journal of Social Structure 3, no. 2: 1-40. 2002.

\bibitem{Snijders2004} Snijders, Tom AB. ``\textit{Models for longitudinal network data,}'' Models and methods in social network analysis 1: 215-247. 2005.

\bibitem{Snijders2010} Snijders, Tom AB., GG Van de Bunt, CEG Steglich, ``\textit{Introduction to stochastic actor-based models for network dynamics,}'' Social networks 32 (1), 44-60. 2010.

\bibitem{Sowe} Sowe, S., L. Stamelos, and L. Angelis, ``\textit{Identifying knowledge brokers that yield software engineering knowledge in OSS projects,}'' Information and Software Technology, vol. 48, pp. 1025-1033, Nov 2006. 

\bibitem{Spence} Spence, M. ``\textit{Job market signaling,}'' Quarterly Journal of Economics, 87: 355-374. 1973.

\bibitem{Steglich} Steglich, C., T. AB Snijders, and M. Pearson. ``\textit{Dynamic networks and behavior: Separating selection from influence,}'' Sociological methodology 40, no. 1: 329-393. 2010.

\bibitem{Storey} Storey, M., L. Singer, B. Cleary, F. Figueira Filho, and A. Zagalsky, ``\textit{The (R) Evolution of social media in software engineering,}'' Proc. Future of Software Engineering, ACM, 2014.

\bibitem{Syeed} Syeed, M. M., ``\textit{Socio-Technical Dependencies in Forked OSS Projects: Evidence from the BSD Family,}'' Journal of Software 9.11 (2014): 2895-2909. 2014.

\bibitem{JoseWebKit} Teixeira, J., and T. Lin, ``\textit{Collaboration in the open-source arena: the webkit case,}'' Proc. 52nd ACM conf. Computers and people research (SIGSIM-CPR '14). ACM, 2014.

\bibitem{Torres} Torres, M. R. M., S. L. Toral, M. Perales, and F. Barrero, ``\textit{Analysis of the Core Team Role in Open Source Communities,}'' Int. Conf. on Complex, Intelligent and Software Intensive Systems, IEEE, 2011. 

\bibitem{Zachary} Zachary, W., ``\textit{An information flow model for conflict and fission in small groups,}'' Journal of Anthropological Research, vol. 33, no. 4, pp. 452-473, 1977.

\end{thebibliography}
